---
title: "Compare Modeled versus Observed Hydrographs using `razviz`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare Modeled versus Observed Hydrographs using `razviz`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

## Introduction
The purpose of this vignette is to demonstrate how to use the [`razviz`](https://mpdougherty.github.io/razviz/) package to produce a `pdf` report of modeled versus observed hydrographs for a set of [HEC-RAS](https://www.hec.usace.army.mil/software/hec-ras/) hydraulic model scenarios. 

## Install
Begin by loading the needed packages. 
```{r setup, message=FALSE}
#install.packages("ggplot2")
library(ggplot2)

#install.packages("reshape2")
library(reshape2)

#install.packages("stringr")
library(stringr)

#install.packages("devtools")
library(devtools)

#install.packages("tidyverse")
library(tidyverse)

#install.packages("readr")
library(readr)

#install.packages("tibble")
library(tibble)

#install.packages("R.utils")
library(R.utils)

#install.packages("readtext")
library(readtext)
```

Next, we'll install the `razviz` package. 
```{r install, eval=FALSE}
devtools::install_github(repo = "mpdougherty/razviz", build_vignettes = TRUE)
```

Finally, we'll load the `razviz` package. 
```{r load_razviz}
library(razviz)
```


#DSS-Vue
dssrip needs to know where DSS is stored on your computer. If you are using DSSVue which was installed from ACE-IT, it will likely be in your programs folder under HEC. If you get errors that your path could not be found, make sure that two back slashes (e.g. \\ ) are included in the path name.  For some, DSS is downloaded into a new location in order to use a more recent version. 

#R profile 
Save a text file called .Rprofile in you documents folder

if(R.Version()$arch=="x86_64"){
  # use 64-bit .jar and .dll
  options(dss_location="C:\\Users\\b6echla0\\Desktop\\HEC-DSSVue-v3.0.00.212\\")
  #options(dss_jre_location="C:\\Users\\b6echla0\\Desktop\\HEC-DSSVue-v3.0.00.212")
  #Sys.setenv(JAVA_HOME=options("dss_jre_location"))  # I think this should be: Sys.setenv(JAVA_HOME=""), but works anyway because not set for 64-bit.
}

```{r DSS Location}
#options(dss_location="C:\\Program Files (x86)\\HEC\\DSSVue")
options("dss_location")
```

#Java
rJava is a hard package to get working. The only way I could get it load was from the default settings. 
```{r}
#install.packages("rJava")
library(rJava)
packageVersion("rJava")
```

#dssrip
Now with all the previous files installed, install dssrip using the code provided in the read me file.  If that does not work, you can download the tar.gz file on to a local drive and install it from there. Often the tar.gz file will be saved in a temporary location and you can copy to a new location from there.

Source: https://github.com/eheisman/dssrip/
Helpful Blog Post (cannot access while on VPN)
http://eaheisman.blogspot.com/2013/04/hec-dss-files-and-r-and-python.html
```{r dssrip install, warning=FALSE}
#devtools::install_github("eheisman/dssrip", INSTALL_opts = "--no-multiarch", ref="r36_rJava0.9-12_fixes",force = TRUE)
library(dssrip)
```

#Troubleshooting
Run these codes to ensure that rJava and DSS are woring through dssrip properly
```{r}
.jinit() #temporary fix
.jclassPath() #should include DSS locations
```

#dssrip 
List the functions which dssrip has available. In July 2020, the developer of dssrip, made changes to the code. Please refer to the github account for updates.
```{r dssrip functions, eval=FALSE}
#List the functions that dssrip has available to use.
lsf.str("package:dssrip")
```

#Read the Unsteady Flow Files
In this step, we need to tell R which paths to take from observed DSS database. HEC-RAS creates an unsteady flow file that lists the observed data which is input in the data for each plan.  

Copy and paste those into a new text file and save it in the working directory folder under the name "UnsteadyFlowObservedDateFile_EVENT.txt" Substitute event for the event year used in each plan. 

NOTE: Option #2 allows you to individually import unsteady flow files. If you are changing more than plan_events in the naming structure, it may be easier to just import the files individually. 
```{r HEC-RAS Unsteady Flow File}
plan_events <- c(2001, 2014, 2019) #Replace with years for each event within the HEC-RAS plans

#Option #1: Automatically import several files
path <- system.file("extdata/hydrographs",
                                package = "razviz")

filelist = list.files(path, pattern="*.txt")

textfiles <- readtext::readtext(paste0(path,"/*.txt"), docvarsfrom = "filepaths")
for(i in 1:length(plan_events)){
  assign(paste0("UnsteadyFlowFile_",plan_events[i]),textfiles$text[i])
}

unsteadyflowfile_list <- mget(ls(pattern="UnsteadyFlowFile_"))

#Option #2 Manually import individual files

#UnsteadyFlowFile_2001 <- readtext::readtext(paste0(path,"/UnsteadyFlowObservedData_2001mod.txt"))
#UnsteadyFlowFile_2014 <- readtext::readtext(paste0(path,"/UnsteadyFlowObservedData_2014.txt"))
#UnsteadyFlowFile_2019 <- readtext::readtext(paste0(path,"/UnsteadyFlowObservedData_2019mod.txt"))
#unsteadyflowfile_list <- list(UnsteadyFlowFile_2001,UnsteadyFlowFile_2014,UnsteadyFlowFile_2019)

#function automatically reformats the text file into useable formats for the rest of the code. 
#function returns a list of dataframes. If you want to see the data within
Formatted_UnsteadyFlowFileList <- razviz::import_unsteadyflowfile(unsteadyflowfile_list = unsteadyflowfile_list,
                                                                  plan_events = plan_events)

#function returns a list of dataframes. If you want to see the data within, use the following code.
example <- Formatted_UnsteadyFlowFileList[[1]]
```



## Import Hydraulic Model Output
In this step we'll import the RAS exports from several RAS model calibration runs. 

```{r}

```









* Use the `razviz::import_ras_hydrographs` function to import the example RAS model results included in the package for each modeled event. 
* Specify the hydrologic event name, the model run number, and the model type. 
* Repeat for each model scenario to be examined. 








### Event 2008, Calibration #9
```{r cal_2008}
# Set event parameters
folder <- system.file("extdata/hydrographs/2008_calibration_9",
                      package = "razviz")
event <- "2008"
run_number <- 9
run_type <- "Calibration"
# Import event model results
cal_2008 <- razviz::import_ras_hydrographs(folder = folder,
                                           event = event,
                                           run_number = run_number,
                                           run_type = run_type)
```

### Event 2013, Calibration #9
```{r cal_2013}
# Set event parameters
folder <- system.file("extdata/hydrographs/2013_calibration_9",
                      package = "razviz")
event <- "2013"
run_number <- 9
run_type <- "Calibration"
# Import event model results
cal_2013 <- razviz::import_ras_hydrographs(folder = folder,
                                           event = event,
                                           run_number = run_number,
                                           run_type = run_type)
```

### Event 2014, Calibration #9
```{r cal_2014}
# Set event parameters
folder <- system.file("extdata/hydrographs/2014_calibration_9",
                      package = "razviz")
event <- "2014"
run_number <- 9
run_type <- "Calibration"
# Import event model results
cal_2014 <- razviz::import_ras_hydrographs(folder = folder,
                                           event = event,
                                           run_number = run_number,
                                           run_type = run_type)
```

### Event 2017, Calibration #9
```{r cal_2017}
# Set event parameters
folder <- system.file("extdata/hydrographs/2017_calibration_9",
                      package = "razviz")
event <- "2017"
run_number <- 9
run_type <- "Calibration"
# Import event model results
cal_2017 <- razviz::import_ras_hydrographs(folder = folder,
                                           event = event,
                                           run_number = run_number,
                                           run_type = run_type)
```

## Combine all model runs and events and recode
In this step we'll get the model results ready for graphing.

* Combine the model events into a single dataset using the `razviz::combine_hydrographs` function. 
* Convert the RAS output from wide format to long format using the `razviz::lengthen_hydrographs` function. 
* Cleanup labels to ensure well-formed plot titles. 

```{r combine_events}
# Combine hydrograph events 
hydrograph_list <- list(cal_2008, cal_2013, cal_2014, cal_2017)
cal_wide <- razviz::combine_hydrographs(hydrograph_list)

# Convert to long format suitable for plotting
cal <- razviz::lengthen_hydrographs(cal_wide)

# Rename factors for prettier plot labeling
cal$River <- forcats::fct_recode(cal$River, 
                                 "Mississippi" = "MISSISSIPPI")
cal$Reach <- forcats::fct_recode(cal$Reach, 
                                 "Big Muddy to Ohio"      = "BIG MUDDY_OHIO", 
                                 "Fox to Bear"            = "FOXTOBEAR",
                                 "Illinois to Mizzou"     = "ILLINOIS_MIZZOU",
                                 "Iowa to Des Moines"     = "IOWATODESM",
                                 "Kaskaskia to Big Muddy" = "KASKY_BIGMUDDY",
                                 "Meramec to Kaskaskia"   = "MERAMEC_KASKY",
                                 "Missouri to Meramec"    = "MISSOURI_MERAMEC",
                                 "North to Salt"          = "NORTHTOSALT",
                                 "Salt to Cuivre"         = "SALT_CUIVRE",
                                 "Wyaconda to Fabius"     = "WYACONDATOFABIUS")

```

## Define hydrograph plot pages
In this step we'll define the pages needed to draw the hydrograph plots. 

```{r plot_pages}
cal_plots <- razviz::hydrograph_plot_pages(cal)
```

## Output Folder
In this step we'll define the output folder.

```{r temp_dir}
output_dir <- "C:/temp"
if (!dir.exists(output_dir)) {dir.create(output_dir)}
```

## Hydrograph Report
In this step we'll cal the hydrograph report. 

* Run the report.
* Check the results in the file: [Hydrograph_Plot_Report.pdf](https://mpdougherty.github.io/razviz/doc/Hydrograph_Plot_Report.pdf)

```{r hydrograph_report, echo=FALSE}
razviz::hydrograph_report(cal, cal_plots, output_dir)
```

