---
title: "Compare Modeled versus Observed Hydrographs using `razviz`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare Modeled versus Observed Hydrographs using `razviz`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

# Introduction
The purpose of this vignette is to demonstrate how to use the `razviz` package to produce a `pdf` report of modeled versus observed hydrographs for a set of [HEC-RAS](https://www.hec.usace.army.mil/software/hec-ras/) hydraulic model scenarios. 

## Install
Begin by loading the needed packages. 
```{r setup}
library(tidyverse)
library(devtools)
```

Next, we'll install the `razviz` package. 
```{r install, eval=FALSE}
devtools::install_github(repo = "mpdougherty/razviz", build_vignettes = TRUE)
```

Finally, we'll load the `razviz` package. 
```{r load_razviz}
library(razviz)
```

## Hydraulic Model Output
In this step we'll import the DSSVue exports from several RAS model calibration runs. 

* Import the example RAS model results in `.csv` format included in the package. 

```{r dssvue_columns}
DSSVue_script_col_types = readr::cols(
                "ModelCrossSection" = col_character(),
                "ModelRiver"        = col_character(),
                "ModelReach"        = col_character(),
                "Date"              = col_character(),
                "Time"              = col_character(),
                "W.S. Elev"         = col_double(),
                "Obs WS"            = col_double(),
                "Modeled Q"         = col_double(),
                "Obs Q"             = col_double())
```

