---
title: "Compare Modeled versus Observed Hydrographs using `razviz`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare Modeled versus Observed Hydrographs using `razviz`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

## Introduction
The purpose of this vignette is to demonstrate how to use the [`razviz`](https://mpdougherty.github.io/razviz/) package to produce a `pdf` report of modeled versus observed hydrographs for a set of [HEC-RAS](https://www.hec.usace.army.mil/software/hec-ras/) hydraulic model scenarios. 

## Install
Begin by loading the needed packages. 
```{r setup, message=FALSE}
library(forcats)
library(devtools)
```

Next, we'll install the `razviz` package. 
```{r install, eval=FALSE}
devtools::install_github(repo = "mpdougherty/razviz", build_vignettes = TRUE)
```

Finally, we'll load the `razviz` package. 
```{r load_razviz}
library(razviz)
```

## Import Hydraulic Model Output
In this step we'll import the RAS exports from several RAS model calibration runs. 

* Use the `razviz::import_ras_hydrographs` function to import the example RAS model results included in the package for each modeled event. 
* Specify the hydrologic event name, the model run number, and the model type. 
* Repeat for each model scenario to be examined. 

### Event 2008, Calibration #9
```{r cal_2008}
# Set event parameters
folder <- system.file("extdata/hydrographs/2008_calibration_9",
                      package = "razviz")
event <- "2008"
run_number <- 9
run_type <- "Calibration"
# Import event model results
cal_2008 <- razviz::import_ras_hydrographs(folder = folder,
                                           event = event,
                                           run_number = run_number,
                                           run_type = run_type)
```

### Event 2013, Calibration #9
```{r cal_2013}
# Set event parameters
folder <- system.file("extdata/hydrographs/2013_calibration_9",
                      package = "razviz")
event <- "2013"
run_number <- 9
run_type <- "Calibration"
# Import event model results
cal_2013 <- razviz::import_ras_hydrographs(folder = folder,
                                           event = event,
                                           run_number = run_number,
                                           run_type = run_type)
```

### Event 2014, Calibration #9
```{r cal_2014}
# Set event parameters
folder <- system.file("extdata/hydrographs/2014_calibration_9",
                      package = "razviz")
event <- "2014"
run_number <- 9
run_type <- "Calibration"
# Import event model results
cal_2014 <- razviz::import_ras_hydrographs(folder = folder,
                                           event = event,
                                           run_number = run_number,
                                           run_type = run_type)
```

### Event 2017, Calibration #9
```{r cal_2017}
# Set event parameters
folder <- system.file("extdata/hydrographs/2017_calibration_9",
                      package = "razviz")
event <- "2017"
run_number <- 9
run_type <- "Calibration"
# Import event model results
cal_2017 <- razviz::import_ras_hydrographs(folder = folder,
                                           event = event,
                                           run_number = run_number,
                                           run_type = run_type)
```

## Combine all model runs and events and recode
In this step we'll get the model results ready for graphing.

* Combine the model events into a single dataset using the `razviz::combine_hydrographs` function. 
* Convert the RAS output from wide format to long format using the `razviz::lengthen_hydrographs` function. 
* Cleanup labels to ensure well-formed plot titles. 

```{r combine_events}
# Combine hydrograph events 
hydrograph_list <- list(cal_2008, cal_2013, cal_2014, cal_2017)
cal_wide <- razviz::combine_hydrographs(hydrograph_list)

# Convert to long format suitable for plotting
cal <- razviz::lengthen_hydrographs(cal_wide)

# Rename factors for prettier plot labeling
cal$River <- forcats::fct_recode(cal$River, 
                                 "Mississippi" = "MISSISSIPPI")
cal$Reach <- forcats::fct_recode(cal$Reach, 
                                 "Big Muddy to Ohio"      = "BIG MUDDY_OHIO", 
                                 "Fox to Bear"            = "FOXTOBEAR",
                                 "Illinois to Mizzou"     = "ILLINOIS_MIZZOU",
                                 "Iowa to Des Moines"     = "IOWATODESM",
                                 "Kaskaskia to Big Muddy" = "KASKY_BIGMUDDY",
                                 "Meramec to Kaskaskia"   = "MERAMEC_KASKY",
                                 "Missouri to Meramec"    = "MISSOURI_MERAMEC",
                                 "North to Salt"          = "NORTHTOSALT",
                                 "Salt to Cuivre"         = "SALT_CUIVRE",
                                 "Wyaconda to Fabius"     = "WYACONDATOFABIUS")

```

## Define hydrograph plot pages
In this step we'll define the pages needed to draw the hydrograph plots. 

```{r plot_pages}
cal_plots <- razviz::hydrograph_plot_pages(cal)
```

## Output Folder
In this step we'll define the output folder.

```{r temp_dir}
output_dir <- "C:/temp"
if (!dir.exists(output_dir)) {dir.create(output_dir)}
```

## Hydrograph Report
In this step we'll cal the hydrograph report. 

* Run the report.
* Check the results in the file: [Hydrograph_Plot_Report.pdf](https://mpdougherty.github.io/razviz/doc/Hydrograph_Plot_Report.pdf)

```{r hydrograph_report, echo=FALSE}
razviz::hydrograph_report(cal, cal_plots, output_dir)
```

